### 2010-06-28 trunk/paper/IIWAS2010/content/results_discussion.tex
changes to results

\begin{tabular}{l | l | r}
Term & Category & $P(Category|Term)$ \\
\hline
1997 & Sedans & 404132.77e-14\\
1997 Toyota & Engines & 7.90e-14\\
Toyota  & Sedans & 3486670.15e-14\\
Toyota Camry & Sedans & 12147.23e-14\\
Toyota Camry V6 & Coupes & 13.80e-14\\
Camry & Sedans & 312034.20e-14\\
Camry V6 & Coupes & 13.80e-14\\
V6 & Sedans & 4464535.40e-14\\
\hline
\end{tabular}

@@

\begin{tabular}{l | r}
Query & Score\\
\hline
A 1997 Toyota Camry V6 needs what size tires? & 0.91\\ 
What is the tire size for a 1998 Sienna XLE Van? & 0.72\\ 
What is the tire size for a 1996 Infiniti I30 Sedan? & 0.88\\ 
\hline
\end{tabular}

\caption{Top ranked queries and relevance scores}
\label{tbl:ranked_queries}

@@

In this paper, we proposed a novel question answering system that uses previously answered user queries to answer similar questions using deep web site.  The system uses a guide user to annotate answer paths so folowing users can discover answers to complicated questions.  Each question answer pair is assigned a realm, and new questions are matched to the new question answer pairs. [How do we calculate relam for a candidate query? and NLP]. This question matching strategy assumes that candidate query terms are available in the category corpus. The candidate query's category annotation will fail if the
query terms are not available in the corpus. In addition, classification of a term or n-gram into a category is based on the term frequency distributions in a classified web document. We are working on improving this
approach by using a probabilistic generative approach as used in the Topic
Models\cite{Blei2003latentdirichlet}.

>>>>

\begin{tabular}{| p{3.2cm} | l | r |}
\hline 
Term & Category & $P(Category|Term)$ \\ \hline
1997 & Sedans & 404132.77e-14\\ 
1997 Toyota & Engines & 7.90e-14\\ 
Toyota  & Sedans & 3486670.15e-14\\ 
Toyota Camry & Sedans & 12147.23e-14\\ 
Toyota Camry V6 & Coupes & 13.80e-14\\ 
Camry & Sedans & 312034.20e-14\\ 
Camry V6 & Coupes & 13.80e-14\\ 
V6 & Sedans & 4464535.40e-14\\ \hline
\end{tabular}

@@

\begin{tabular}{| p{3.5cm} | p{3cm} | r |}
\hline
Query & Tagged Categories & Score\\ \hline
A 1997 Toyota Camry V6 needs what size tires? & IC:Sedans, Cars, Engines, Manufactures OC:size tires & 0.91\\ \hline 
What is the tire size for a 1998 Sienna XLE Van? & IC:Vans, Manufactures OC: tire size & 0.72\\ \hline 
Where can I buy an engine for a Toyota Camry V6? & IC:Manufactures, Sedans, Engines OC: where & - \\ \hline 
What is the cost of a Toyota Camry V6 engine? &  IC:Manufactures, Sedans, Engines OC: the clost  & - \\ \hline
\end{tabular}

\caption{Top ranked queries and relevance scores: IC - input categories, OC - output categories}
\label{tbl:ranked_queries}

@@

In this paper, we proposed a novel question answering system that uses previously 
answered user queries to answer similar questions using deep web site.  
The system uses a guide to annotate answer paths so folowing users 
can discover answers to complicated questions.  Each question answer pair is 
assigned a realm, and new questions are matched to the new question answer pairs. 
This query matching strategy assumes that candidate query terms are
available in the category corpus. The candidate query's category annotation will
fail if the query terms are not available. In addition, classification of a
term or n-gram into a category is based on the term frequency distributions in a
classified web document. We are working on improving this
approach by using a probabilistic generative approach as used in the Topic
Models\cite{Blei2003latentdirichlet}.
